\artikel{Facilities at the TU Darmstadt}
{In this article you will learn about some of the most important facilities at the TU Darmstadt.
}{
    \textbf{Departments and fields of study}

    Numerous scientific disciplines and engineering fields, organized into various departments and fields of study, are present at the TU Darmstadt.
    There are 13 departments with numbers ranging from 1 to 20, For example department 1 for law and economic science, department 18 for electrical engineering and department 20 for computer science. Some numbers are unassigned, for example there is no department 19. Additionally, a field of study, such as Computational Engineering, is built around a single study program. These are much smaller than the departments and their scientific profile is more narrow than that of a department.

    Departments and fields of study are at the top level of the organizational structure. Each department again is divided into a number of research groups that focus on a specific area of their department's scientific profile. But even those research groups may be divided into smaller groups that consist of a group leader and his assistants.

    The head of each department is the Dean, a professor of the department. He is the director of the department and head of the Dean's office, which administrates and publicly represents the department.
    Additionally, there is a Dean of Studies who is responsible for the administration of teaching and therefore often more important for students.\\

    \textbf{Administration and Presidium}

    The university may be divided into different departments with their own rules and structures but they still form one large structure. Similar to the deans of the departments there is a formal head of the university -- the president, who heads the presidium. The latter consists of seven parts (German: Dezernate), each of which is responsible for a part of the administration. Dezernat II for example is responsible for examinations and coordinates exam dates and rooms for all departments.

    Another part of the administration is the Office of Student Affairs which is the first contact point for students' administrative issues, for example if your address changes or you need attestation by the university. Even more interesting for you is the International Office that you should already have made contact with. They take care of for international students and also offer specialized assistance.\\

    \textbf{Service units}

    There are more service units for students: the HRZ responsible for administrating the IT-infrastructure of the university and the e-Learning center which offers recordings of lectures. You can also rent projectors and screens there.

    While not a part of the university, the Studentenwerk Darmstadt (Darmstadt student services organisation) is still highly important. It runs the cafeterias and most student residential establishments. They also offer assistance in many ways, like legal advice, psychological services and specialized services for international students like ComeTUgether. Another facility is the University Sports Center that offers a lot of courses for students.

    Last but not least, there is the university and state library which serves as a library for the university but also as the main archive for the state of Hessen.\\

    \textbf{Research}

    Apart from the research and teaching performed at TU Darmstadt, there are several research facilities not part of the university, but in some ways associated with it.
    Some of them offer practical labs and other university courses, jobs for students, as well as cooperation on research subjects. For us computer scientists the Fraunhofer Institutes for Computer Graphics Research (IGD) and for Secure Information Technology (SIT), as well as the Center for Advanced Security Research Darmstadt (CASED) are of most interest.
}
{Stefan Gries\\ edited and translated by Johannes Alef}
%\newpage
