\addsec{Checklist for your first week(s) at the TU Darmstadt}

\subsection*{During the orientation phase}

\checkbox{Received welcome-bag}{You get this bag at the welcome event during the orientation phase. If you couldn't participate in this event you can also get it in the room of the student council D120 in the Piloty-Building.}

\checkbox{Attended the student advisory service talk}{This talk is held on Tuesday. It is very important for your studies!}


\subsection*{Accounts}

\checkbox{Activated HRZ-Account}{If you didn't do this in the orientation phase already, follow the steps on \footnotemark[1]. The initial password is the one from the letter that came with your student id card.}

\checkbox{Activated ISP/RBG-Account}{If you didn't do this in the orientation phase already, log in under \footnotemark[2] with your HRZ-Username and password, and follow the steps to activate your ISP/RBG-Account.}

\checkbox{Log in to the Computer Science Moodle}{You can log in with your HRZ-data: on \footnotemark[3] use the button "`Login"' and then "`Anmeldung mit TU-ID"'.}


\newpage

\subsection*{Registrations}

\checkbox{Registered in TUCaN for modules.}{On Tuesday you get to learn how to use TUCaN.}

\checkbox{Registered in TUCaN for courses.}{After you registered for the modules you must register for the associated courses. Only if you have done this you can register for exams during the exams registration phase.}

\checkbox{Checked imposed conditions.}{Ensure that you know where to register for your imposed conditions and make sure to pass them quickly.}

\subsection*{Sonstiges}

\checkbox{Upload a picture for the Athene-card.}{To get the Athene-card, you have to upload a picture fulfilling the specified requirements under [4]. This picture gets printed on your Athene-card. If you can't upload a picture you can also check [5] for dates where you can go to get that photo made and uploaded.}



\footnotetext[1]{\url{https://dwi.nds.tu-darmstadt.de/stud/activateLogin.vtlr}}
\footnotetext[2]{\url{https://support.rbg.informatik.tu-darmstadt.de}}
\footnotetext[3]{\url{https://moodle.informatik.tu-darmstadt.de}}
\footnotetext[4]{\url{https://www.idm.tu-darmstadt.de/ando}}
\footnotetext[5]{\url{https://www.hrz.tu-darmstadt.de/id/athenekarte_neu/ak_foto/}}


\newpage
