\addsec{Common Abbreviations}

\textbf{Explanations for some of the most common abbreviations at the TU Darmstadt. Here you can look up important information again.}

\begin{longtable}{p{20mm}p{85mm}}
    APB          & General Examination Terms (German: Allgemeine Prüfungsbestimmungen) is the document regulating everything for exams and studies.                                                                                                                         \\
    AStA         & The general committee of students (German: Allgemeiner Studierendenausschuss) is elected by the student parliament and has several departments (social matters, finances, Fachschaften (student councils), international students, university politics). \\
    B.Sc.        & Bachelor of Science. The first academic title.                                                                                                                                                                                                           \\
    CE           & Computational Engineering. A study program that combines computer science, mathematics, mechanical and electrical engineering.                                                                                                                           \\
    c.t.         & cum tempore. Meaning you may be late up to fifteen minutes for a meeting. At the TU Darmstadt s.t. is the norm.                                                                                                                                          \\
    FB           & The German abbreviation for department (German: Fach-bereich). There are 13 different departments at the TU Darmstadt, computer science having the highest number (20).                                                                                  \\
    FBR          & The department council (German: Fachbereichsrat) is where professors, students and administrative staff make decisions for the department.                                                                                                               \\
    FS           & Abbreviation for the student council (German: Fachschaft).                                                                                                                                                                                               \\
    GnoM         & Games no Machines, a board and/or card game get-together of the computer science students. (No electronic devices allowed!)                                                                                                                              \\
    HRZ          & Administration of the IT-Infrastructure of the TU Darmstadt. Responsible for the Athene-card and WLAN.                                                                                                                                                   \\
    ISP          & Administration of the IT-Infrastructure of the computer science department.                                                                                                                                                                              \\
    LiWi/LW      & Campus of the TU Darmstadt on the outskirts of Darmstadt: Lichtwiese. There is not much of interest for computer science students except for the beer garden in the summer.                                                                              \\
    LZM          & Learning Centre for mathematics. Here you can find scripts, exercises and answers relating to mathematics lectures.                                                                                                                                      \\
    M.Sc.        & Master of Science. The academic title after the B. Sc.                                                                                                                                                                                                   \\
    Piloty       & Robert-Piloty-Building (Building S2$|$02) = the main building for computer science students.                                                                                                                                                             \\
    RBG          & The old name of the ISP.                                                                                                                                                                                                                                 \\
    RMV          & Our local public transport company: Rhein-Main-Verkehrsverbund.                                                                                                                                                                                          \\
    SFK          & A student group organizing a movie screening twice a week in the Audimax.                                                                                                                                                                                \\
    SS n/SoSe n  & Summer term of the year n.                                                                                                                                                                                                                               \\
    s.t.         & sine tempore. You must not be late. Opposite of c.t.                                                                                                                                                                                                     \\
    StuPa        & Student parliament.                                                                                                                                                                                                                                      \\
    TUCaN        & TU-Campus-Net. Central administration of courses, modules, exams and corresponding grades. It is important to be registered in time, especially for exams.                                                                                               \\
    TU Darmstadt & Technical University Darmstadt.                                                                                                                                                                                                                          \\
    ULB          & The library of the TU Darmstadt (German: Universitäts- und Landesbibliothek). The building is near the cafeteria.                                                                                                                                        \\
    USZ          & The University Sports centre (German: Unisportzentrum) is in building S3$|$03. Here you can register for the sports courses offered.                                                                                                                     \\
    WS m/n       & Winter term beginning in October of year m and ending in March year n.                                                                                                                                                                                   \\
    ZSB          & Central Student advisory Service. For general questions, not computer science specific.                                                                                                                                                                  \\
\end{longtable}
