\artikel{Commented schedule}
{On the front inlay of this booklet you can find the schedule for the orientation phase. In this article the different entries shall be explained a little further.}
{\textbf{Plenumevents}

The Cyber-Orentation-Phase starts on monday at 10 a.m. with a welcome meeting from the department. Here we’ll explain to you in more detail what the orientation phase is about and what you can expect from it. On monday and tuesday there are some live interviews with professors about the fields of study available to you, where you also may ask questions yourselves. On monday evening from 16 p.m. we planed a studying q\&a, where you can ask seasond master-students about their or rather your studies.\\

\noindent\textbf{AStA Talk}

The AStA ("Allgemeiner Studierendenausschuss", \textit{general committee of students}) represents the interests of TU Darmstadt's students on several of the university's boards. In addition, they offer a lot of services for students, like legal and other advice, as well as other offers specific for international students. In this talk, an AStA representative will provide you with more information on what they are and do.\\

\noindent\textbf{IT Infrastructure}

Several institutions within TU Darmstadt and the department of computer science are responsible for the local computer and network infrastructure. In this talk you'll hear about these institutions and what you need to know about them and how they can be useful to assist with your studies.\\

\noindent\textbf{City-Tour}

On Tuesday from 2 p.m. we will go through Darmstadt with a camera. We show you the most important places and explain them to you. Of course you can look up these informations later anytime.\\

\noindent\textbf{Fun and Freetime}

This semester is digital, so we host a game night on monday from 5 p.m. and tuesday from 4 p.m. for example with Minecraft, Counter-Strike and a few more. While you play together, you can socialize with your new fellow students.
}{}
